
\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[top=0.7in, bottom=0.7in, left=0.7in, right=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{parskip}
\setlength{\parindent}{0pt}
% Removed invalid \titlespacing* for starred sections
\renewcommand{\baselinestretch}{1.05}

% Compact header
\begin{document}
\vspace*{-1.2cm}
\begin{center}
    {\LARGE \textbf{Alyssa Peck}} \\
    123 Love Lane, Pleasantville, USA $\vert$ (555) 123-4567 $\vert$ \href{mailto:alyssa1peck@gmail.com}{alyssa1peck@gmail.com} $\vert$ \href{https://linkedin.com/in/graceharper}{linkedin.com/in/graceharper}
\end{center}
\vspace{-0.5em}

% Summary
\textbf{CPA with 9 years' experience leading global cross-functional teams, driving digital finance transformation, and optimizing processes. Passionate about aligning financial operations with strategic goals through automation, analytics, and continuous improvement.}
\vspace{0.5em}

% --- Experience ---
\section*{Experience}
\textbf{Ernst \& Young, San Jose, CA} \hfill \textit{Aug 2023--Present}\\
Assurance Senior Manager \,\textbar\, Digital Advisor\\
\textit{Previously: Manager, Digital Coach, Senior, Associate (Aug 2016--Aug 2023)}
\begin{itemize}[leftmargin=*, itemsep=0.2em, topsep=0.2em]
    \item Led global audits for Fortune 100 tech clients, managing teams of 8--15 and collaborating with diverse stakeholders, including international and offshore teams.
    \item Owned and led digital transformation for EY's Apple account; coached teams on GenAI, Alteryx, Power BI, and global tools adoption.
    \item Led audit adoptions of new standards (ASC 842, ASC 606); experienced in complex technical accounting (stock-based comp, leases, investments, revenue, convertible debt).
    \item Ensured SOX 404 compliance by understanding business/IT processes and providing best practice recommendations.
    \item Developed and deployed 15+ custom digital tools, including a dashboard now used by engagement teams across the US.
    \item Built end-to-end data pipelines for key insights on financial metrics, trends, and correlations.
    \item Drove transformation of data tooling to improve process efficiency and accuracy; worked with IT to provision new systems for software tools.
    \item Communicated results to Audit Committee to align financial reporting with enterprise risk/governance frameworks.
    \item Recognized as a high performer with early promotions and external recognition (SF Business Times/CAL CPA Next Gen in Accounting).
    \item Coordinated 20+ global statutory audits annually, supporting 50+ more; traveled internationally to coach teams on best practices.
    \item Trained and supervised junior staff on US GAAP, regulatory matters, and digital audit methodology.
    \item Ensured compliance with deadlines by reorganizing priorities, adjusting workloads, and restructuring teams.
\end{itemize}
\textbf{Industry:} Tech (SaaS), Retail

% --- Education ---
\section*{Education}
\textbf{Santa Clara University, Santa Clara, CA} \hfill \textit{B.S. Accounting, Minor in Entrepreneurship, June 2016}

% --- Skills & Certifications ---
\section*{Skills \& Certifications}
\begin{multicols}{2}
\textbf{Certifications:}
\begin{itemize}[leftmargin=*, itemsep=0.1em, topsep=0.1em]
    \item CPA, California (145179)
    \item AICPA member
    \item EY Digital Silver Badge
    \item Alteryx Designer Core Cert.
    \item Lean Six Sigma White Belt
\end{itemize}

\textbf{Skills:}
\begin{itemize}[leftmargin=*, itemsep=0.1em, topsep=0.1em]
    \item US GAAP
    \item Digital Transformation/Automation (AI, RPA)
    \item Global Process Optimization
    \item SOX 404 Compliance \& Risk Mitigation
    \item Cross-Functional Leadership
    \item Data Analytics
\end{itemize}

\textbf{Systems:}
\begin{itemize}[leftmargin=*, itemsep=0.1em, topsep=0.1em]
    \item SAP, NetSuite, Power BI, Power Automate (RPA), Alteryx (ETL)
    \item Microsoft 365, Copilot, Blackline, Workday, Coupa
    \item AuditBoard, Asana, Box, DataSnipper, SQL
\end{itemize}
\end{multicols}

% --- Awards ---
\section*{Awards}
\begin{itemize}[leftmargin=*, itemsep=0.1em, topsep=0.1em]
    \item Pleasantville "Heart of Gold" Award (2022)
    \item Teacher of the Year, Pleasantville Elementary (2012)
    \item Volunteer of the Month, Pleasantville Community Center (multiple years)
\end{itemize}

% --- References ---
\section*{References}
Available upon request.

\end{document}
